### 2019-10-03 thesis/txt2/2-background.tex
first complete draft thesis introduction, chapters and structure in separate files

\section{Background}

\subsection{semi-structured data}
characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access (for developers here! -> impact on our work with buildlogs) \cite{abiteboul1997querying}

>>>>

\chapter{Background}

\section{semi-structured data}
characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access (for developers here! -> impact on our work with buildlogs) \cite{abiteboul1997querying}
